### 2019-01-22 journal/experiments.tex
small change

>>>>

Alternatively, a radical way to produce ``hot'' mutants at low cost (the only significant cost being that of executing the test suite to throw out mutants killed by some passing test) is to produce mutants at the \emph{object code} level, which does not require recompiling a system.  This is how SQLite applies mutation testing:  \url{https://www.sqlite.org/testing.html#mutation_testing}.  Object level mutants are obviously not useful (or at least, certainly not \emph{as} useful) for fault localization as source-level mutants, but they mutating branches alone probably captures many compiler repairs that are useful in fuzzer taming.
